---
title: "NE Lakeshore TMDL, stream monitoring and ag datasets"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: lumen
    source_code: embed
---

```{r setup}, include=FALSE}
library(leaflet)
library(rgdal)
library(crosstalk)
library(viridis)
#devtools::install_github("dmurdoch/leaflet@crosstalk4")
setwd("C:/Users/oldenk/Desktop/subbasins_R_data")
subbasin<-readOGR(".","subbasin_update")

subbasin1 <- spTransform(subbasin, CRS("+init=epsg:4326"))

subbasin1@data$TP<-as.numeric(levels(subbasin1@data$TP))[subbasin1@data$TP]
subbasin1@data$TSS<-as.numeric(levels(subbasin1@data$TSS))[subbasin1@data$TSS]
subbasin1@data$TN<-as.numeric(levels(subbasin1@data$TN))[subbasin1@data$TN]
subbasin1@data$order_<-as.numeric(levels(subbasin1@data$order_))[subbasin1@data$order_]

subbasin1@data$TP_avg_lb_<-as.numeric(levels(subbasin1@data$TP_avg_lb_))[subbasin1@data$TP_avg_lb_]
subbasin1@data$TSS_avg_lb<-as.numeric(levels(subbasin1@data$TSS_avg_lb))[subbasin1@data$TSS_avg_lb]
subbasin1@data$count<-as.numeric(levels(subbasin1@data$count))[subbasin1@data$count]


subbasin1@data$TotLbP2acR<-round(subbasin1@data$TotLbP2acR)
subbasin1@data$TSS_avg_lb<-round(subbasin1@data$TSS_avg_lb)
subbasin1@data$TP_avg_lb_<-round(subbasin1@data$TP_avg_lb_,digits=2)
 


df1 = as.data.frame(subbasin1@data)[, c(18:20,22,24)]       # extract desired columns into a data.frame
df1[is.na(df1)] <- 0                             # change values that are zero into NA
subbasin1@data[1:NROW( subbasin1@data),c(18:20,22,24)] = df1 #put back into spacial dataframe

county<-readOGR(".","counties")
county <- spTransform(county, CRS("+init=epsg:4326"))

lakes<-readOGR(".","lakes")
lakes <- spTransform(lakes, CRS("+init=epsg:4326"))

streams<-readOGR(".","2018_2020_streams")
streams <- spTransform(streams, CRS("+init=epsg:4326"))

mon<-readOGR(".","monitoring_locations_results")
mon <- spTransform(mon, CRS("+init=epsg:4326"))

basin<-readOGR(".","trib_basin")
basin <- spTransform(basin, CRS("+init=epsg:4326"))


blue_stream<-readOGR(".","non_impired_fill_in")
blue_stream <- spTransform(blue_stream, CRS("+init=epsg:4326"))

               
sd <-  SharedData$new(subbasin1)
sd_df <- SharedData$new(subbasin1@data, group = sd$groupName())

mycols<-c("#5557ac",
"#61b63a",
"#9748bd",
"#4fb867",
"#472288",
"#bdb437",
"#6c6de0",
"#97b24d",
"#d04aac",
"#57c3a9",
"#c83e2e",
"#4cc3de",
"#ce6428",
"#6d8fe4",
"#e19a37",
"#32134c",
"#94b57b",
"#cf7ede",
"#31571c",
"#d64a88",
"#40855b",
"#d53e5d",
"#329faf",
"#862f23",
"#6fa4db",
"#9f782a",
"#38356e",
"#737e30",
"#903077",
"#cc9c6d",
"#42689e",
"#e07c67",
"#5f2150",
"#754b24",
"#ca97ce",
"#74253c",
"#8a5d94",
"#cf778e",
"#cf778e"	)

mycols2<-c("#d83f57",
"#a8484e",
"#e38378",
"#cf4d2c",
"#995c2c",
"#d97f2f",
"#d99c69",
"#dfa93b",
"#a1852c",
"#626223",
"#b3bb31",
"#b5b767",
"#868e4e",
"#647e22",
"#7db838",
"#509936",
"#57c759",
"#76b978",
"#3c8143",
"#2a6a45",
"#38bf79",
"#3a9779",
"#56cbb0",
"#3ebbcb",
"#549dd1",
"#3d69b3",
"#598bea",
"#6664d4",
"#9f95db",
"#675a9c",
"#b15dd5",
"#9c59ae",
"#da8dcc",
"#d34bad",
"#9a537c",
"#bd3479",
"#e66d98",
"#8a8687",
"#8a8687")


```

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}
filter_slider("Manure P2O5 Application (lb/P2O5/year)", "Manure P2O5 Application (lb/P2O5/year)", sd_df,column= ~TotLbP2acR)
filter_slider("Median soil phosphorus (ppm)", "Median soil phosphorus (ppm)", sd_df,column= ~median)
filter_slider("TP: Median growing season conc., in Watershed", "TP: Median growing season conc., in Watershed", sd_df,column= ~TP)
filter_slider("TP: Pounds per acre, in Watershed", "TP: Pounds per acre, in Watershed", sd_df,column= ~TP_avg_lb_,min=0)
filter_slider("TSS: Median growing season conc., in Watershed", "TSS: Median growing season conc., in Watershed", sd_df,column= ~TSS)
filter_slider("TSS: Pounds per acre, in Watershed", "TSS: Pounds per acre, in Watershed", sd_df,column= ~TSS_avg_lb)
filter_slider("TN: Median growing season conc., in Watershed", "TN: Median growing season conc., in Watershed", sd_df,column= ~TN)
#potential have to throw in extra slider so map doesn't glitch.
filter_slider("Ignore this", "Ignore this", sd_df,column= ~TN)



```




Row 
-------------------------------------

### 
This iteractive map shows the following datasets:

- Median growing season (May - Oct) concentration of TP, TSS, and TN between 2017 - 2019 from stream monitoring (2016 - 2019 for Ahnapee at Washington, Silver at Willow (near Algoma), and 3 LTT sites at mouth of Kewaunee, Manitowoc, and Sheboygan)
- Stream loads per acre for TP and TSS from stream monitoring 
- Medain soil P concentration per subbasin, from CAFO NMPs
- Average manure P2O5 spreading (lb/ac/year) per subbasin, from WDNR analysis
- Layer titled "FILTERED RESULTS" will show which subbasins meet the criteria of the filter sliders in the left column. 

Tips:

- Layers are transparent; however, layering multiple datasets results in colors that cannot be directly interpreted 
- Turn on the FILTERED RESULTS layer (with all other watershed layers off) to see which subbasins meet the criteria specified with the filter sliders (left column)
- Most layers have more information when hovering cursor over the map

```{r, out.width='100%', out.height='100%'}

#manure p2O5 prep
bins <- c(0,50, 60, 70, 80, 90,100,110,120,130)
pal <- colorBin("YlOrRd", domain = subbasin1$TotLbP2acR, bins = bins)
labels <- sprintf(
  "<strong> Watershed: %s</strong><br/>lb manure P2O5 per yr: %g<br/>Subbasin: %g",
  subbasin1$mon_basin, subbasin1$TotLbP2acR,subbasin1$Subbasin) %>% lapply(htmltools::HTML)

#soil p prep
bins1 <-c(0,10,20,30, 40, 50,100,180) 
pal1 <-colorBin("YlOrRd", domain=subbasin1$median,bins = bins1)
labels1 <- sprintf(
  "<strong> Watershed: %s</strong><br/>Median soil P (ppm): %g<br/>Sample count: %g<br/>Q1: %g<br/>Q3: %g<br/>Subbasin: %s</strong>",
  subbasin1$mon_basin, subbasin1$median, subbasin1$count, subbasin1$Q1, subbasin1$Q3,subbasin1$Subbasin) %>% lapply(htmltools::HTML)



#TP prep 
bins2<-c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)
pal2 <-colorBin("YlOrRd", domain=subbasin1$TP,bins = bins2)
labels2 <- sprintf(
  "<strong> Watershed: %s</strong><br/>Subbasin: %s</strong><br/>TP - growing season median (mg/L): %g",
  subbasin1$mon_basin,subbasin1$Subbasin, subbasin1$TP) %>% lapply(htmltools::HTML)

#TP load ac prep 
bins2a<-c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7,0.8,0.9,1,1.5,2,2.5)
pal2a <-colorBin("YlOrRd", domain=subbasin1$TP_avg_lb_,bins = bins2a)
labels2a <- sprintf(
  "<strong> Watershed: %s</strong><br/>Subbasin: %s</strong><br/>lb TP per acre (mg/L): %g",
  subbasin1$mon_basin,subbasin1$Subbasin, subbasin1$TP_avg_lb_) %>% lapply(htmltools::HTML)


#TSS prep 
bins3<-c(0, 2,4,6,8,10,12,14,16,18,20,22,24,26,28,30)
pal3 <-colorBin("YlOrRd", domain=subbasin1$TP,bins = bins3)
labels3 <- sprintf(
  "<strong> Watershed: %s</strong><br/>Subbasin: %s</strong><br/>TSS - growing season median (mg/L): %g",
  subbasin1$mon_basin,subbasin1$Subbasin, subbasin1$TSS) %>% lapply(htmltools::HTML)

#TSS load ac prep 
bins3a<-c(0,10,20,30,40,50,60,70,80,90,100,150,200,250,300)
pal3a <-colorBin("YlOrRd", domain=subbasin1$TSS_avg_lb,bins = bins3a)
labels3a <- sprintf(
  "<strong> Watershed: %s</strong><br/>Subbasin: %s</strong><br/>lb TSS per acre (mg/L): %g",
   subbasin1$mon_basin,subbasin1$Subbasin, subbasin1$TSS_avg_lb) %>% lapply(htmltools::HTML)

#TN prep 
bins4<-c(0, 1, 2, 3, 4, 5, 6, 7,8)
pal4 <-colorBin("YlOrRd", domain=subbasin1$TP,bins = bins4)
labels4 <- sprintf(
  "<strong> Watershed: %s</strong><br/>Subbasin: %s</strong><br/>TN - growing season median (mg/L): %g",
  subbasin1$mon_basin,subbasin1$Subbasin, subbasin1$TN) %>% lapply(htmltools::HTML)

#TP circle prep
labels6<-sprintf(
  "<strong>  %s</strong><br/>TP - growing season median (mg/L):%g<br/># of samples: %g<br/>Q1 (mg/L): %g<br/>Q3 (mg/L): %g",
  mon$station__1, mon$TP_median,mon$TP_count, mon$TP_q1, mon$TP_q3)%>% lapply(htmltools::HTML)

#TSS circle prep
labels7<-sprintf(
 "<strong>  %s</strong><br/>TSS - growing season median (mg/L):%g<br/># of samples: %g<br/>Q1 (mg/L): %g<br/>Q3 (mg/L): %g",
  mon$station__1, mon$TSS_median,mon$TSS_count, mon$q1, mon$TSS_q3)%>% lapply(htmltools::HTML)

#TN circle prep
labels8<-sprintf(
 "<strong> %s</strong><br/>TN - growing season median (mg/L):%g<br/># of samples: %g<br/>Q1 (mg/L): %g<br/>Q3 (mg/L): %g",
  mon$station__1, mon$TN_median,mon$TN_count, mon$TN_q1, mon$TN_q3)%>% lapply(htmltools::HTML)

#filter prep
n<-rainbow(39)
#pal5<-colorFactor(sample(rainbow(39)), domain=subbasin1$mon_basin)
pal5<-colorFactor(palette=mycols2, domain=subbasin1$order_)
labels5 <- sprintf(
  "<strong>Watershed: %s</strong><br/>Subbasin: %s",
  subbasin1$mon_basin,subbasin1$Subbasin) %>% lapply(htmltools::HTML)

#blue - delist
 #brown - sediment
 #red - phosphorus
#yellow - sediment & P
             
#impaired waters prep
impair_cols<-c("Blue", 
               "#7D692A",
               "#F12B0C",
               "orange") #brown sediment & P
label9<-sprintf("<strong> %s</strong><br/>Pollutant: %s",
                streams$Label,streams$Pollutant_)%>% lapply(htmltools::HTML)
               

pal6<-colorFactor(palette=impair_cols, domain=streams$Pollutant_)

p = colorFactor(palette =c("Blue","Brown","Red","Orange"),domain= c("Delist","Sediment (TSS)","Phosphorus","Phosphorus & Sediment (TSS)"),ordered= TRUE)


#impaired lakes prep
label10<-sprintf("<strong> %s</strong>",
                lakes$WATERBODY_)%>% lapply(htmltools::HTML)


#montitoring stations labels
label11<-sprintf("<strong> %s</strong><br/>Monitoring type:%s<br/>",
mon$station__1,mon$summary)%>% lapply(htmltools::HTML)

map=leaflet(sd)  %>% 
  addTiles(group = "Street View") %>% 
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") %>%
  setView(lng = -87.870196, lat=44.104887,zoom=9) %>% 
  addPolylines(data=county,
              color="grey",
              opacity=0.8,
              group="Boundary: County")%>%
    addPolylines(data=basin,
             color = "black",
             weight=2,
             opacity=.8,
             group="Boundary: Major trib basins")%>%
  
  addPolylines(data=streams,
               color=~pal6(Pollutant_),
               weight=1.5,
               opacity = .8,
               label=label9,
               group="2020 Impaired Streams (TP & TSS)",
                            highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = TRUE),
             labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                        textsize = "15px",
                                        direction = "auto"))%>%
    addPolylines(data=blue_stream,
               weight=1.5,
               color="blue",
               opacity = 0.8,
               group="Unimpaired Streams (major)")%>%
   addPolygons(data=lakes,
              color="red",
              fillOpacity=.7,
              group="2020 Impaired Lakes (TP)",
              label=label10,
               highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = TRUE),
             labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                        textsize = "15px",
                                        direction = "auto"))%>%


  addCircleMarkers(data=mon,
             radius=mon@data$TP_median*50,
             color="#0e6e0b",
             group="TP: Median growing season conc., at Location",
            label = labels6,
            #highlight = highlightOptions(weight = 5,
             #                              color = "#666",
              #                             dashArray = "",
               #                            fillOpacity = 0.7,
                #                           bringToFront = TRUE),
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
  
    #stream TP
  addPolygons(data=subbasin1,
             fillColor=ifelse(test=subbasin1@data$TP==0,yes="grey",no=pal2(subbasin1@data$TP)),
              weight = 1,
              opacity = 1,
              color = "white",
              dashArray = "1",
              fillOpacity = 0.5,
              group="TP: Median growing season conc., in Watershed",
              highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = FALSE),
              label = labels2,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
  
  #stream TP per ac
  addPolygons(data=subbasin1,
              #fillColor=~pal2a(TP_avg_lb_),
              fillColor=ifelse(test=subbasin1@data$TP_avg_lb_==0,yes="grey",no=pal2a(subbasin1@data$TP_avg_lb)),
              weight = 1,
              opacity = 1,
              color = "white",
              dashArray = "1",
              fillOpacity = 0.5,
              group="TP: lb per acre, in Watershed",
              highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = FALSE),
              label = labels2a,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
  addCircleMarkers(data=mon,
             radius=mon@data$TSS_median*1.5,
            color="#52442d",
            label = labels7,
            group="TSS: Median growing season conc., at Location",
            #highlight = highlightOptions(weight = 5,
             #                              color = "#666",
              #                             dashArray = "",
               #                            fillOpacity = 0.7,
                #                           bringToFront = TRUE),
             labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                        textsize = "15px",
                                        direction = "auto")) %>%
    #stream TSS
  addPolygons(data=subbasin1,
              #fillColor=~pal3(TSS),
              fillColor=ifelse(test=subbasin1@data$TSS==0,yes="grey",no=pal3(subbasin1@data$TSS)),
              weight = 1,
              opacity = 1,
              color = "white",
              dashArray = "1",
              fillOpacity = 0.5,
              group="TSS: Median growing season conc., in Watershed",
              highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = FALSE),
              label = labels3,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
  
  #stream TSS per ac
  addPolygons(data=subbasin1,
              #fillColor=~pal3a(TSS_avg_lb),
              fillColor=ifelse(test=subbasin1@data$TSS_avg_lb==0,yes="grey",no=pal3a(subbasin1@data$TSS_avg_lb)),
              weight = 1,
              opacity = 1,
              color = "white",
              dashArray = "1",
              fillOpacity = 0.5,
              group="TSS: lb per acre, in Watershed",
              highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = FALSE),
              label = labels3a,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
  addCircleMarkers(data=mon,
             radius=mon@data$TN_median*5,
             color="red",
             group="TN: Median growing season conc., at Location",
            label = labels8,
            #highlight = highlightOptions(weight = 5,
             #                              color = "#666",
              #                             dashArray = "",
                #                           fillOpacity = 0.7,
               #                            bringToFront = TRUE),
            labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                         textsize = "15px",
                                          direction = "auto")) %>%
    #stream TN
  addPolygons(data=subbasin1,
              #fillColor=~pal4(TN),
              fillColor=ifelse(test=subbasin1@data$TN==0,yes="grey",no=pal4(subbasin1@data$TN)),
              weight = 1,
              opacity = 1,
              color = "white",
              dashArray = "1",
              fillOpacity = 0.5,
              group="TN: Median growing season conc., in Watershed",
              highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = FALSE),
              label = labels4,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
  
  
#manure
  addPolygons(data=subbasin1,
              fillColor=~pal(TotLbP2acR),
              weight = 1,
              opacity = 1,
              color = "white",
              dashArray = "1",
              fillOpacity = 0.5,
              group="Manure P2O5 (lb/ac/year) - WDNR Analysis",
              highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = FALSE),
              label = labels,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
  #soil P
  addPolygons(data=subbasin1,
              fillColor=~pal1(median),
              weight = 1,
              opacity = 1,
              color = "white",
              dashArray = "1",
              fillOpacity = 0.5,
              group="Median Soil P (ppm) - CAFO NMPs",
              highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = FALSE),
              label = labels1,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
  
    addCircles(data=mon,
             radius=30,
             color="black",
             opacity=1,
             group="Monitoring Locations and Activity",
                         highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = TRUE),
             label=label11,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                         textsize = "15px",
                                          direction = "auto")) %>%



  
  #Filtered Results
  #no 'data' argument is important, otherwise, filtered results will not disply in this layer
  addPolygons(
              fillColor=~pal5(order_),
              weight = 1,
              opacity = 1,
              color = "white",
              dashArray = "1",
              fillOpacity = 0.5,
              group="FILTERED RESULTS",
              highlight = highlightOptions(weight = 5,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = FALSE),
              label = labels5,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px",
                                          direction = "auto")) %>%
 
  #blue - delist
 #brown - sediment
 #red - phosphorus
#yellow - sediment & P
   #Stream impaired legend


  addLegend("bottomleft", pal=p, values=c("Delist","Sediment (TSS)","Phosphorus","Phosphorus & Sediment (TSS)"), title="2020 impaired streams",group="2020 Impaired Streams (TP & TSS)") %>%
  #Manure legend
  addLegend("bottomright", pal = pal, values = ~TotLbP2acR,
          title = "lb P2O5 per receiving <br> acre per year",
          opacity = .5,
        group = "Manure P2O5 (lb/ac/year) - WDNR Analysis") %>%
  #soil P legend
  addLegend("bottomleft", pal = pal1, values = ~median,
            title = "Median Soil P (ppm)",
            opacity = .5,
            group = "Median Soil P (ppm) - CAFO NMPs") %>%
  #stream TP legend
  addLegend("bottomleft", pal =pal2, values =~TP,
            title = "TP - growing season median (mg/L)",
            opacity = .5,
            group="TP: Median growing season conc., in Watershed") %>%
  #stream lb TP ac legend
  addLegend("bottomleft", pal = pal2a, values = ~TP_avg_lb_,
            title = "lb TP per acre",
            opacity = .5,
            group = "TP: lb per acre, in Watershed") %>%
  #stream TSS legend
  addLegend("bottomleft", pal = pal3, values = ~TSS,
            title = "TSS - growing season median (mg/L)",
            opacity = .5,
            group = "TSS: Median growing season conc., in Watershed") %>%
  #stream lb TSS ac legend
  addLegend("bottomleft", pal = pal3a, values = ~TSS_avg_lb,
            title = "lb TSS per ac",
            opacity = .5,
            group = "TSS: lb per acre, in Watershed") %>%
  #stream TN legend
  addLegend("bottomleft", pal = pal4, values = ~TN,
            title = "TN - growing season median (mg/L)",
            opacity = .5,
            group = "TN: Median growing season conc., in Watershed") %>%
  
  addLayersControl(
    baseGroups = c("Street View", "Satellite"),
    overlayGroups=c('Manure P2O5 (lb/ac/year) - WDNR Analysis','Median Soil P (ppm) - CAFO NMPs','TP: Median growing season conc., in Watershed','TP: Median growing season conc., at Location','TP: lb per acre, in Watershed','TSS: Median growing season conc., in Watershed','TSS: Median growing season conc., at Location','TSS: lb per acre, in Watershed','TN: Median growing season conc., in Watershed','TN: Median growing season conc., at Location','Boundary: County','Boundary: Major trib basins','2020 Impaired Streams (TP & TSS)' ,'Unimpaired Streams (major)', '2020 Impaired Lakes (TP)','FILTERED RESULTS','Monitoring Locations and Activity' ),
    options = layersControlOptions(collapsed = FALSE))%>%

hideGroup(c('Manure P2O5 (lb/ac/year) - WDNR Analysis','Median Soil P (ppm) - CAFO NMPs','TP: Median growing season conc., in Watershed','TP: lb per acre, in Watershed','TSS: Median growing season conc., in Watershed','TSS: Median growing season conc., at Location','TSS: lb per acre, in Watershed','TN: Median growing season conc., in Watershed','TN: Median growing season conc., at Location', '2020 Impaired Lakes (TP)','FILTERED RESULTS','Monitoring Locations and Activity'))  # turn these off by default


map


```





